\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-01 letter.tex
add paragraph on E6 to letter

Editor's point $\#$6: I have removed the duplicate statement of Assumption 1. [{\color{blue} much more to do here}]

>>>>

Editor's point $\#$6: I have rewritten the passage about the influence of lobbying on the executive to read
\begin{quote}
  This setup does not strictly require that the executives are not lobbied. The assumption that the weight the executives place on import-competing profits is constant only requires that the extent to which they favor this industry cannot be \textit{directly} influenced by lobbying effort. The assumption is innocuous as long as the executives' preferences are not directly altered in a significant way by lobbying over trade.
\end{quote}
I think this is a softer claim than what was in the earlier draft and avoids getting into an interpretation of exactly what `Protection for Sale' means in this context since this is not central---what is important is to defend the modeling assumption directly.

I have also removed the duplicate statement of Assumption 1 and combined redundant text surrounding the two statements. I have added $\forall e$ to the statement of Assumption 1.
